%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Page Two Column Resume based off deedy_resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% Modified by: sanchagrins
% https://github.come/sanchagrins
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{sanchagrins-resume}
\usepackage{fancyhdr}
\usepackage{fontspec}
\usepackage{fontawesome}

 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Stephen}{Sanchagrin}{{\href{mailto:sanchagrins@gmail.com}{\faEnvelope \hspace{2mm} sanchagrins@gmail.com} | {\href{https://sanchagrins.github.io}{\faGlobe \hspace{2mm}sanchagrins.github.io}} | {\href{https://github.com/sanchagrins}{\faGithub \hspace{2mm}sanchagrins}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\topsep} 
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\runsubsection{University of Maryland - University College}\\
\descript{BS in Computer Science}
\location{May 2018 (Expected) | Adelphi, MD}
\location{GPA: 4.0 / 4.0 }
\sectionsep

\runsubsection{East Carolina University}\\
\descript{MA in History}
\location{May 2014 | Greenville, NC}
\location{GPA: 3.78 / 4.0}
\sectionsep

\runsubsection{East Carolina University}\\
\descript{BS in Applied Geography}
\location{Dec 2007 | Greenville, NC}
Magna Cum Laude\\
\location{GPA: 3.73 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\runsubsection{Proficient:}\\
Java, Python, Go, \\
Git, Maven, JUnit, \\ 
TDD/Unit Testing,\\
React, Node, Django,\\
Heroku, HTML, CSS, \\
Bootstrap, JSON, LaTex, \\
Linux
\vspace{\topsep}\\
\runsubsection{Familiar:}\\
C++, Agile, MariaDB,\\
MongoDB, AWS, \\
Shell Scripting \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Coursework
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework} 
Data Structures, Algorithms, Advanced Programming Languages,
Operating Systems, Computer Systems Architecture,
Linear Algebra, Discrete Math, Object Oriented and Concurrent Programming 

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Certifications} 
%CompTIA Security +
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
{\href{https://github.com/sanchagrins}{\faGithub \hspace{2mm}github.com/sanchagrins}}\\
{\href{https://www.linkedin.com/in/sanchagrins}{\faLinkedinSquare \hspace{2mm}linkedin.com/in/sanchagrins}}\\
{\href{https://sanchagrins.github.io}{\faGlobe \hspace{2mm}sanchagrins.github.io}}


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.63\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Dewberry, LLC}\descript{ | Geospatial Analyst (Python/Agile)}
\location{Aug 2013 – Sep 2014 | Fairfax, VA}
\vspace{\topsep}
\begin{tightemize}
\item Restructured company hydrodynamic inundation model process by incorporating Python and spatial statistical libraries.
\item Decreased model runtime through automation and optimization by roughly 50\%.
\item Delivered high value projects (\$150k+) on time and under budget.
\item Published map services to cloud based hosting platforms.
\end{tightemize}

\sectionsep
\runsubsection{RENCI@ECU}\descript{ | Geospatial Analyst (Python)}
\location{May 2008 – Jun 2012 | Greenville, NC}
\begin{tightemize}
\item Developed complex geospatial models with Python and spatial statistical software of coastal processes.
\item Analyzed model spatial resolution using a Monte Carlo simulation.
\item Web development (HTML, CSS, JS).
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\runsubsection{Okami Cryptocurrency Tracker}
\descript{| Project Manager\\React / Node / MariaDB / Heroku / Git }
\begin{tightemize}
\item Supervised 5-developer team.
\item Designed application architecture and deployment strategy.
\end{tightemize}
\sectionsep

\runsubsection{Go Neural Net}
\descript{| Developer\\Go / Git }
\begin{tightemize}
\item Implemented two-layer neural network.
\item Utilized back-propagation for weight adjustment with Sigmoid activation function.
\item Developed a custom Linear Algebra library.
\end{tightemize}
\sectionsep

\runsubsection{Django Slack Invite}
\descript{| Developer \\Python / Django / Selenium / Heroku / Git}
\begin{tightemize}
\item A barebones Django app for automating the invite process for Slack.
\item Easily deployable with integrated Heroku support.
\item Designed utilizing Test Driven Design (TDD) and Selenium.
\item Documentation created with Sphinx.
\end{tightemize}
\sectionsep

\runsubsection{Java GUI-Compiler}
\descript{| Developer\\Java Swing / Maven / JUnit / Git}
\begin{tightemize}
\item Custom parser and lexer developed for a BNF GUI grammar.
\item Reads in a source file and builds custom Java Swing GUIs.
\item Dependency resolution, unit testing and artifact creation handled with Maven.
\end{tightemize}
\sectionsep

%\runsubsection{Class Project}
%\descript{| Java / Maven / JUnit}
%\begin{tightemize}
%\item Makes data request to NOAA National Buoy Data Center and calculates descriptive statistics from buoy data.
%\item Dependency resolution, unit testing and artifact creation handled with Maven.
%\end{tightemize}
%\sectionsep

\runsubsection{CS Resume Reddit Bot}
\descript{| Developer\\Python / Tesseract / MongoDB / Git }
\begin{tightemize}
\item Reddit bot that scrapes a popular Computer Science sub-reddit for resumes.
\item Resumes are preprocessed with a custom image filter and parsed with the open source Tesseract Optical Character Recognition Engine.
\item Extracted data is stored in a MongoDB and analyzed using descriptive statistics.
\end{tightemize}
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
